Central Slot Value Extraction from Internet for Wikipedia Entities

### 2013-10-29 paper/flairs27/content/results.tex
Updating paper independent of trek kba terminology

\begin{table}
\caption{Document Chunks Distribution }
\centering
\label{table:documentsDist}

@@

\hline 
\end{tabular} 
\end{table}

@@

\begin{table}
\caption{Benchmark Server Specifications }
\centering
\label{table:serverspec}
\begin{tabular}{|c|l|}
\hline 
\textbf{Spec} & \textbf{Details} \\ \hline
Model & Dell xxx 32 cores \\ \hline 
OS & CentOS release 6.4 Final \\ \hline 
Software Stack & GCC version 4.4.7, Java 1.7.0\_25, Scala 2.9.2, SBT 0.12.3 \\ \hline 
 RAM & 64GB\\ \hline 
 Drives & 2x2.7TB disks, 6Gbps, 7200RPM\\ \hline 
\end{tabular} 
\end{table}

@@

\begin{tabular}{|c|c|c|c|}
\hline 
 & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Sampling \#1 & 55\% & 17\% & 27\% \\ 
\hline Sampling \#2 & 54\% & 15\% & 31\%  \\ 
\hline 
\end{tabular} 
\end{table}

\begin{table}
\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|l|c|c|c|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline

\end{tabular} 
\end{table}

>>>>

\begin{table*}
\caption{Document Chunks Distribution }
\centering
\label{table:documentsDist}

@@

\hline 
\end{tabular} 
\end{table*}

@@

\begin{table}
\caption{Benchmark Server Specifications }
\centering
\label{table:serverspec}
\begin{tabular}{| c | p{5cm} |}
\hline 
\textbf{Spec} & \textbf{Details} \\ \hline
Model & Dell xxx 32 cores \\ \hline 
OS & CentOS release 6.4 Final \\ \hline 
Software Stack & GCC version 4.4.7, Java 1.7.0\_25, Scala 2.9.2, SBT 0.12.3 \\ \hline 
 RAM & 64GB\\ \hline 
 Drives & 2x2.7TB disks, 6Gbps, 7200RPM\\ \hline 
\end{tabular} 
\end{table}

@@

\begin{tabular}{ | c | c | p{2cm} | p{13mm} |}
\hline 
 & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Sampling \#1 & 55\% & 17\% & 27\% \\ 
\hline Sampling \#2 & 54\% & 15\% & 31\%  \\ 
\hline 
\end{tabular} 
\end{table}

\begin{table*}    
\caption{Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
\centering
\label{table:finalresultrecall}
\begin{tabular}{|l|p{3.5cm}|p{4cm}|}
\hline 
 \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

\end{tabular} 
\end{table*}

\begin{table*}
\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|l|c|c|c|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline

\end{tabular} 
\end{table*}

### 2013-10-29 paper/flairs27/paper.tex
added the paper for FLAIRS27. It needs a LOT of work
Updating paper independent of trek kba terminology

\documentclass[10pt]{article}

\usepackage{xcolor}
\usepackage{cite }
\usepackage{graphicx, epsfig}
\usepackage[margin=1in]{geometry}
\usepackage[hyphens]{url}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\title{University of Florida Knowledge Base Acceleration Notebook}

@@

\author{Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{University of Florida, Gainesville, Florida, USA}\\
       {\{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu}
\and
  Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
       {mpetrovic@ihmc.us}
}

@@

\bibliographystyle{unsrt}
\bibliography{citation}

>>>>

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{xcolor}
\usepackage{cite }
\usepackage{graphicx, epsfig}
\usepackage[margin=1in]{geometry}
\usepackage[hyphens]{url}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}

    \usepackage{cite}
    \usepackage{natbib}

@@

\title{Central Slot Value Extraction from Internet for Wikipedia Entities}

@@

\author{Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang\footnote{University of Florida, Gainesville, Florida, USA}, Milenko Petrovic\footnote{Institute for Human and Machine Cognition, Ocala, Florida, USA}\\
       \\
       {\{msnia, cgrant, ypeng, daisyw\}@cise.ufl.edu,}
       {mpetrovic@ihmc.us}
}

@@

\bibliography{citation}
\bibliographystyle{aaai}
